%-------------------------
% Resume in Latex
% Based off of: https://github.com/sb2nov/resume
% and Jake Gutierrez's version of it
% at https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% inspired by https://practicaltypography.com/resumes.html
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[margin = 0.5in]{geometry}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{wrapfig}
\usepackage{graphicx}

%--------------UNDERLINING---------------
% taken from https://alexwlchan.net/2017/10/latex-underlines/

\usepackage{contour}
\usepackage{ulem}

\renewcommand{\ULdepth}{3.8pt}
\contourlength{0.8pt}
\color{darkgray}

\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

%----------------------------------------

\graphicspath{ {./Images/} }

%----------FONT OPTIONS----------
\usepackage{fontspec}
\usepackage{fontawesome5}

% I could have just used the charter package here for the font I wanted...
% but I'd still need to change compiler to XeLaTeX to include the title font
% \usepackage{charter}

\setmainfont{XCharter}

\newfontfamily{\OpenSansRegular}{OpenSans-Regular}[
Path = Fonts/,
Extension = .ttf,
UprightFont = OpenSans-Regular
]

\newfontfamily{\OpenSansBold}{OpenSans-Bold}[
Path = Fonts/,
Extension = .ttf,
UprightFont = OpenSans-Bold
]

\newfontfamily{\OpenSansItalic}{OpenSans-Italic}[
Path = Fonts/,
Extension = .ttf,
UprightFont = OpenSans-Italic
]

\newfontfamily{\OpenSansSemiBold}{OpenSans-SemiBold}[
Path = Fonts/,
Extension = .ttf,
UprightFont = OpenSans-SemiBold
]

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\iffalse
% \iftrue
\addtolength{\oddsidemargin}{0.3in}
\addtolength{\marginparsep}{0.3in}
\addtolength{\evensidemargin}{0.3in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{0.3in}
\addtolength{\textheight}{0.3in}
\fi

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{1pt}\scshape\raggedright\OpenSansBold\Large
    }{}{0pt}{}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \OpenSansSemiBold{#1} & \OpenSansRegular{#2} \\
      \OpenSansItalic{\small#3} & \OpenSansItalic{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\OpenSansRegular}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

{\OpenSansBold \Huge Lucy Hao}

\href{mailto:hao.lucyy@gmail.com}{
    \faEnvelope
    \thinspace \thinspace
    \myuline{\OpenSansRegular hao.lucyy@gmail.com}} $|$
\href{https://linkedin.com/in/lucy-hao}{
    \faLinkedin
    \thinspace \thinspace        
    \myuline{\OpenSansRegular linkedin.com/in/lucy-hao}} $|$
\href{https://github.com/lhao03}{
    \faGithub
    \thinspace \thinspace
    \myuline{\OpenSansRegular lhao03}} $|$
\href{https://lhao03.github.io}{
    \faLaptop
    \thinspace \thinspace
    \myuline{\OpenSansRegular lhao03.github.io}} 

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of British Columbia}{ Sep 2019 - May 2023}
      {Bachelor of Science in Computer Science and minor in Biochemistry}{ cGPA: 3.90/4.33}
  \resumeSubHeadingListEnd
  
%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineering Intern}{May 2021 - now}
      {\href{https://www.microsoft.com/en-us/garage/}{Microsoft - Garage Team}}{}
      \resumeItemListStart
        \resumeItem{The  \href{https://www.microsoft.com/en-us/garage/}{\myuline{Garage internship}} offers a small number of talented students a unique opportunity to work with each other in teams, hack on contemporary technology, conduct customer research, design, and develop a product in 12-16 weeks.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer Co-op}{Jan - May 2021}
      {\href{http://www.proofcentre.ca/}{PROOF (Prevention of Organ Failure) Centre of Excellence}}{}
      \resumeItemListStart
        \resumeItem{Redesigned a  fragile natural language processing pipeline to be more robust to extract patient information from any type of clinical note. Implemented in Python using pandas, nltk, scispaCy, spaCy and regular patterns. Helped publish a \href{https://www.medrxiv.org/content/10.1101/2021.05.04.21256134v1}{\myuline{preprint on medRxiv.}}}
        \resumeItem{Introduced algorithms to auto-correct optical character recognition errors for features of interest (FoI), increasing accuracy for an FoI by {\OpenSansBold 5-10\%}. Added a training module to automatically find the best pipeline parameters in training period.}
        \resumeItem{Abstracted parts of pipeline to be able to generalize on any type of clinical note. Reduced encoding code-base size by over {\OpenSansBold 50\%} while maintaining or increasing pipeline accuracy. Achieved {\OpenSansBold 91\%} validation accuracy on 100 unseen clinical notes.}
        \resumeItem{Gave weekly presentations to medical professionals, faculty members and data scientists to show progress on pipeline and request feedback.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Computer Science Teaching Assistant}{Jan - Apr 2021}
      {University of British Columbia}{}
      \resumeItemListStart
        \resumeItem{Led {\OpenSansBold 3} labs for CPSC 210 (Software Construction) of overall {\OpenSansBold 20} students.}
        \resumeItem{Held office hours to help students learn about Test Driven Design, Java and Object Orientated programming.}
        \resumeItem{Invigilated, marked, and tested exam questions.}
      \resumeItemListEnd
      
       \iffalse
      % \iftrue
    \resumeSubheading
      {yeet}{yeet}
      {yeet}{yeet}
      \resumeItemListStart
        \resumeItem{yeet}
        \resumeItem{yeet}
        \resumeItem{yeet}
      \resumeItemListEnd
      
    \resumeSubheading
      {yeet}{yeet}
      {yeet}{yeet}
      \resumeItemListStart
        \resumeItem{yeet}
        \resumeItem{yeet}
        \resumeItem{yeet}
      \resumeItemListEnd
\fi

  \resumeSubHeadingListEnd

%-----------EXTRA-----------
\section{Extracurricular}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Director of Outreach and Technology}{Sep 2020 - now}
      {StarHacks}{}
      \resumeItemListStart
        \resumeItem{Led outreach operations of the first iteration of \href{https://www.starhacks.tech/starhacks-i}{\myuline{StarHacks}} (female and non-binary virtual hackathon), bringing in  {\OpenSansBold 800+ }registrants and {\OpenSansBold 350+} attendees in the span of 3 months. Grew Instagram followers by {\OpenSansBold 300\%} (414 to {\OpenSansBold 1250+})}
        \resumeItem{Sent monthly newsletters with MailChimp and posted original content designed with Figma and Canva on Instagram and Twitter. Moderated Discord and set up Discord bots to remind hackers of events and automate role assignment.}
      \resumeItemListEnd

    \resumeSubheading
      {Co-lead Software Developer}{Sep 2020 - now}
      {UBC BEST}{}
      \resumeItemListStart
        \resumeItem{Co-leading team of {\OpenSansBold 5-10} students on the development of a cross-platform mobile app that aims to gamify the rehabilitation process for multiple sclerosis patients.}
        \resumeItem{Implemented workflows in GitHub Actions. Mobile app developed using Kotlin Multi-platform and backend developed using MongoDB and Express.}
      \resumeItemListEnd
             \iffalse
      % \iftrue
    \resumeSubheading
      {yeet}{yeet}
      {yeet}{yeet}
      \resumeItemListStart
        \resumeItem{yeet}
        \resumeItem{yeet}
        \resumeItem{yeet}
      \resumeItemListEnd

    \resumeSubheading
      {yeet}{yeet}
      {yeet}{yeet}
      \resumeItemListStart
        \resumeItem{yeet}
        \resumeItem{yeet}
        \resumeItem{yeet}
      \resumeItemListEnd
      \fi
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{Speaking and Awards}
      \resumeItemListStart
        \resumeItem{{\OpenSansBold Speaking}: \href{https://www.linkedin.com/posts/joytojob_students-technology-webinar-activity-6798041515332562944-sGOh}{\myuline{JoytoJob Panel}}, \href{https://www.starhacks.tech/starhacks-i}{\myuline{StarHacks Workshop Host}}}
        \resumeItem{{\OpenSansBold Awards}: Finalist and Realtor Best Search Experience Award at cmd-f 2019, Voiceflow Award at nwHacks 2019}
      \resumeItemListEnd

%-------------------------------------------
\end{document}
