%-------------------------
% Resume in Latex
% Based off of: https://github.com/sb2nov/resume
% and Jake Gutierrez's version of it
% at https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% inspired by https://practicaltypography.com/resumes.html
% License : MIT
%------------------------
%!TeX program = xelatex

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[margin = 0.5in]{geometry}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{wrapfig}
\usepackage{graphicx}

%--------------UNDERLINING--
% taken from https://alexwlchan.net/2017/10/latex-underlines/

\usepackage{contour}
\usepackage{ulem}

\renewcommand{\ULdepth}{3.8pt}
\contourlength{0.8pt}
\color{darkgray}

\newcommand{\myuline}[1]{%
	\uline{\phantom{#1}}%
	\llap{\contour{white}{#1}}%
}

%---------------------------

\graphicspath{ {./Images/} }

%----------FONT OPTIONS-----
\usepackage{fontspec}
\usepackage{fontawesome5}

% I could have just used the charter package here for the font I wanted...
% but I'd still need to change compiler to XeLaTeX to include the title font
% \usepackage{charter}

\newfontfamily{\OpenSansRegular}{OpenSans-Regular}[
	Path = Fonts/,
	Extension = .ttf,
	UprightFont = OpenSans-Regular
]

\newfontfamily{\OpenSansBold}{OpenSans-Bold}[
	Path = Fonts/,
	Extension = .ttf,
	UprightFont = OpenSans-Bold
]

\newfontfamily{\OpenSansItalic}{OpenSans-Italic}[
	Path = Fonts/,
	Extension = .ttf,
	UprightFont = OpenSans-Italic
]

\newfontfamily{\OpenSansSemiBold}{OpenSans-SemiBold}[
	Path = Fonts/,
	Extension = .ttf,
	UprightFont = OpenSans-SemiBold
]

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\iffalse
	% \iftrue
	\addtolength{\oddsidemargin}{0.3in}
	\addtolength{\marginparsep}{0.3in}
	\addtolength{\evensidemargin}{0.3in}
	\addtolength{\textwidth}{-0.5in}
	\addtolength{\topmargin}{0.3in}
	\addtolength{\textheight}{0.3in}
\fi

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{1pt}\scshape\raggedright\OpenSansBold\Large
}{}{0pt}{}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\OpenSansSemiBold{#1} & \OpenSansRegular{#2} \\
		\OpenSansItalic{\small#3} & \OpenSansItalic{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\OpenSansRegular{\small#1} & \OpenSansRegular{#2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
		\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\OpenSansRegular}
		\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%---------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

{\OpenSansBold \Huge Lucy Hao}

\href{mailto:hao.lucyy@gmail.com}{
	\faEnvelope
	\thinspace \thinspace
	\myuline{\OpenSansRegular hao.lucyy@gmail.com}} $|$
\href{https://linkedin.com/in/lucy-hao}{
	\faLinkedin
	\thinspace \thinspace
	\myuline{\OpenSansRegular linkedin.com/in/lucy-hao}} $|$
\href{https://github.com/lhao03}{
	\faGithub
	\thinspace \thinspace
	\myuline{\OpenSansRegular lhao03}} $|$
\href{https://lhao03.github.io}{
	\faLaptop
	\thinspace \thinspace
	\myuline{\OpenSansRegular lhao03.github.io}}

%-----------EDUCATION--------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of British Columbia}{ Sep 2019 - May 2024 (Expected)}
{B.Sc Combined Computer Science and Chemistry}{cGPA: 3.90/4.33}
\resumeSubHeadingListEnd


%------------Research--------
\section{Research Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{http://www.proofcentre.ca/}{PROOF (Prevention of Organ Failure) Centre of Excellence}}{Jan - May 2021}
{Software Developer Co-op}{Vancouver, Canada}
\resumeItemListStart
\resumeItem{Redesigned a fragile natural language processing pipeline to extract patient information from any type of clinical note with pre-trained word embeddings. Implemented in Python using pandas, nltk, scispaCy, spaCy, and regular expressions.}
\resumeItem{Reduced the encoding code-base size by over {\OpenSansBold 50\%} through abstraction while increasing pipeline accuracy. Achieved {\OpenSansBold 91\%} validation accuracy.}
\resumeItem{Published: Chen, Y., Hao, L., Zou, V.Z., Hollander, Z., Ng, R.T., Isaac, K.V.
	{\href{https://doi.org/10.1186/s12874-022-01583-z}{Automated medical chart review for breast cancer outcomes research: a novel natural language processing extraction system.}}
		{\OpenSansItalic BMC Med Res Methodol 22}, 136 (2022).}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Teaching---------

\section{Teaching Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Systematic Program Design (CPSC 110)}{Winter 2021}
{Computer Science Teaching Assistant}{}
\resumeItemListStart
\resumeItem{Led labs, graded exams/problem sets, and taught concepts from functional programming and data driven programming in Racket.}
\resumeItem{Received {\OpenSansBold90\%+} evaluation score during Winter 2021 term.}
\resumeItemListEnd

\resumeSubheading
{Software Construction (CPSC 210)}{Winter 2020, Summer 2021}
{Computer Science Teaching Assistant}{}
\resumeItemListStart
\resumeItem{Led labs, invigilated and graded exams, and graded final projects, and taught concepts such as test driven design, design patterns and object oriented programming in Java.}
\resumeItem{Received {\OpenSansBold perfect} evaluation score during Summer 2021 term.}
\resumeItem{Received {\OpenSansBold80\%+} evaluation score during Winter 2020 term.}
\resumeItemListEnd

\resumeSubHeadingListEnd
%----------------------------

%------------Industry--------
\section{Industry Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{}{Capital One}}{Jun - Aug 2022}
{Software Engineering Intern}{New York, United States}
\resumeItemListStart
\resumeItem{Piloted use of AWS Device Farm to create end-to-end testing for Mobile App Verification (MAV).}
\resumeItem{Wrote tests for Capital One mobile app using Java and Appium and Capital One website using Python and Selenium. Eliminated {\OpenSansBold 100\%} of unnecessary idling on AWS by using threads in test scripts.}
\resumeItemListEnd

\resumeSubheading
{\href{https://www.microsoft.com/en-us/garage/}{Microsoft}}{May - Aug 2021}
{Software Engineering Intern (Garage Program)}{Vancouver, Canada}
\resumeItemListStart
\resumeItem{Collaborated with a team of 6 interns to plan and develop an internal team requested feature in React, Redux, and TypeScript which allowed developers to efficiently and easily try out the Microsoft Graph API.}
\resumeItem{Presented technical architectural diagrams to developers and developed proof of concepts to decide on technical designs. Added static analysis tools and pre-commit hooks, saving time for PR reviews.}
\resumeItem{Refactored the Teams App code-base, removing over {\OpenSansBold 500+} lines. Found bug regarding different Microsoft account types within Graph Explorer and had the fix merged into the live production application.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------Publications-----------
% \section{Publications}
% \resumeItemListStart
% \resumeItem{Chen, Y., Hao, L., Zou, V.Z., Hollander, Z., Ng, R.T., Isaac, K.V.
% 	Automated medical chart review for breast cancer outcomes research: a novel natural language processing extraction system.
% 		{\OpenSansItalic BMC Med Res Methodol 22}, 136 (2022).}
% \resumeItemListEnd

%----------------------------

%-----------Extracurricular--

\section{Extracurricular}
\resumeItemListStart
\resumeItem{
	Director of Outreach and Technology at StarHacks {\OpenSansItalic(2020-2022)},
	Marketing Co-Director at nwPlus {\OpenSansItalic(2021-2022)},
	Joytojob Panelist {\OpenSansItalic(2021)},
	StarHacks Workshop Host {\OpenSansItalic(2021/2022)},
	Citro Hacks Workshop Host {\OpenSansItalic(2021)},
	Hydrangea Hacks Workshop Host {\OpenSansItalic(2021)},
	Hacking 4 Community Panelist {\OpenSansItalic(2021)},
	HackCamp Workshop Host {\OpenSansItalic(2021)}
}
\resumeItemListEnd

%----------------------------

\end{document}
