%-------------------------
% Resume in Latex
% Based off of: https://github.com/sb2nov/resume
% and Jake Gutierrez's version of it
% at https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% inspired by https://practicaltypography.com/resumes.html
% License : MIT
%------------------------
%!TeX program = xelatex

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[margin = 0.5in]{geometry}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{wrapfig}
\usepackage{graphicx}

%--------------UNDERLINING---------------
% taken from https://alexwlchan.net/2017/10/latex-underlines/

\usepackage{contour}
\usepackage{ulem}

\renewcommand{\ULdepth}{3.8pt}
\contourlength{0.8pt}
\color{darkgray}

\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

%----------------------------------------

\graphicspath{ {./Images/} }

%----------FONT OPTIONS----------
\usepackage{fontspec}
\usepackage{fontawesome5}

% I could have just used the charter package here for the font I wanted...
% but I'd still need to change compiler to XeLaTeX to include the title font
% \usepackage{charter}

\setmainfont{XCharter}

\newfontfamily{\OpenSansRegular}{OpenSans-Regular}[
Path = Fonts/,
Extension = .ttf,
UprightFont = OpenSans-Regular
]

\newfontfamily{\OpenSansBold}{OpenSans-Bold}[
Path = Fonts/,
Extension = .ttf,
UprightFont = OpenSans-Bold
]

\newfontfamily{\OpenSansItalic}{OpenSans-Italic}[
Path = Fonts/,
Extension = .ttf,
UprightFont = OpenSans-Italic
]

\newfontfamily{\OpenSansSemiBold}{OpenSans-SemiBold}[
Path = Fonts/,
Extension = .ttf,
UprightFont = OpenSans-SemiBold
]

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\iffalse
% \iftrue
\addtolength{\oddsidemargin}{0.3in}
\addtolength{\marginparsep}{0.3in}
\addtolength{\evensidemargin}{0.3in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{0.3in}
\addtolength{\textheight}{0.3in}
\fi

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{1pt}\scshape\raggedright\OpenSansBold\Large
    }{}{0pt}{}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \OpenSansSemiBold{#1} & \OpenSansRegular{#2} \\
      \OpenSansItalic{\small#3} & \OpenSansItalic{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \OpenSansRegular{\small#1} & \OpenSansRegular{#2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\OpenSansRegular}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

{\OpenSansBold \Huge Lucy Hao}

\href{mailto:hao.lucyy@gmail.com}{
  \faEnvelope
  \thinspace \thinspace
  \myuline{\OpenSansRegular hao.lucyy@gmail.com}} $|$
\href{https://linkedin.com/in/lucy-hao}{
  \faLinkedin
  \thinspace \thinspace
  \myuline{\OpenSansRegular linkedin.com/in/lucy-hao}} $|$
\href{https://github.com/lhao03}{
  \faGithub
  \thinspace \thinspace
  \myuline{\OpenSansRegular lhao03}} $|$
\href{https://lhao03.github.io}{
  \faLaptop
  \thinspace \thinspace
  \myuline{\OpenSansRegular lhao03.github.io}}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of British Columbia}{ Sep 2019 - May 2023 (Expected)}
{Bachelor of Science in Computer Science and minor in Biochemistry}{ cGPA: 3.90/4.33}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Garage Software Engineering Intern}{May 2021 - now}
{\href{https://www.microsoft.com/en-us/garage/}{Microsoft}}{}
\resumeItemListStart
\resumeItem{The  \href{https://www.microsoft.com/en-us/garage/}{\myuline{Garage internship}} offers a small number of talented students a unique opportunity to work with each other in teams, hack on contemporary technology, conduct customer research, design, and develop a product in 12-16 weeks.}
\resumeItemListEnd

\resumeSubheading
{Software Developer Co-op}{Jan - May 2021}
{\href{http://www.proofcentre.ca/}{PROOF (Prevention of Organ Failure) Centre of Excellence}}{}
\resumeItemListStart
\resumeItem{Redesigned a  fragile natural language processing pipeline to be more robust to extract patient information from any type of clinical note. Implemented in Python using pandas, nltk, scispaCy, spaCy and regular patterns. Helped publish a \href{https://www.medrxiv.org/content/10.1101/2021.05.04.21256134v1}{\myuline{preprint on medRxiv.}}}
\resumeItem{Introduced algorithms to auto-correct optical character recognition errors for features of interest (FoI), increasing accuracy for an FoI by {\OpenSansBold 5-10\%}. Added a training module to automatically find the best pipeline parameters in training period.}
\resumeItem{Abstracted parts of pipeline to be able to generalize on any type of clinical note. Reduced encoding code-base size by over {\OpenSansBold 50\%} while maintaining or increasing pipeline accuracy. Achieved {\OpenSansBold 91\%} validation accuracy on 100 unseen clinical notes.}
\resumeItem{Gave weekly presentations to medical professionals, faculty members and data scientists to show progress on pipeline and request feedback.}
\resumeItemListEnd

\resumeSubheading
{Computer Science Teaching Assistant}{Jan - Apr 2021}
{University of British Columbia}{}
\resumeItemListStart
\resumeItem{Led {\OpenSansBold 3} labs for CPSC 210 (Software Construction) of overall {\OpenSansBold 20} students.}
\resumeItem{Held weekly office hours to help students learn about Test Driven Design, Java and Object Orientated programming.}
\resumeItem{Invigilated, marked, and tested exam questions.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{{\href{https://devpost.com/software/seniors-chat}{\myuline{\OpenSansBold Dialogue}}} $|$ {JavaScript, MongoDB, Express.js, WebRTC, Heroku, Git, Figma}}{Jan 2021}
\resumeItemListStart
\resumeItem{In team of 4, developed a full-stack web application using Express.js and MongoDB for the backend and React for the frontend.}
\resumeItem{Used MongoDB to store user's info and created algorithem to match users with similar interests.}
\resumeItem{Implemented video calling functionality with socket.io, WebRTC in the browser. Deployed on Heroku.}
\resumeItem{Average score of{\OpenSansBold{~80-90\%}} from peer judges.}
\resumeItemListEnd
\resumeProjectHeading
{{\href{https://devpost.com/software/ecoeats-sgwzhp}{\myuline{\OpenSansBold EcoEats (Finalist)}}} $|$ {Google Cloud Vision API, Java, Android, Git, Figma}}{Mar 2020}
\resumeItemListStart
\resumeItem{In 24 hours as lead programmer of a group of 4, developed an Android app in Java that brings awareness to the carbon footprint of consumers' meals and advocates for more carbon-friendly products.
}
\resumeItem{Uses Google Cloud Vision API to analyze photos of food. Presented project to all participants and judges as finalists among {\OpenSansBold 200+} hackers. Awarded Realtor Best Search Experience and Wolfram Award.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Extracurricular-----------

\section{Extracurricular}
\resumeItemListStart
\resumeItem{{\OpenSansBold Speaking}: \href{https://www.linkedin.com/posts/joytojob_students-technology-webinar-activity-6798041515332562944-sGOh}{\myuline{JoytoJob Panel}}, \href{https://www.hydrangeahacks.tech/}{\myuline{Hydrangea Hacks Workshop Host}}, \href{https://www.starhacks.tech/starhacks-i}{\myuline{StarHacks Workshop Host}}, \href{https://citro.tech/citrohacks/index.html}{\myuline{Citro Hacks Workshop Host}}}
\resumeItem{{\OpenSansBold Community}: Director of Outreach and Technology at \href{https://www.starhacks.tech/}{\myuline{StarHacks}}, Marketing Coordinator at \href{https://www.nwplus.io/}{\myuline{nwPlus}}, mentor at AIHacks and Superposition, mentor for connect-f 2020}
\resumeItemListEnd

%-------------------------------------------
\end{document}
